\textbf{COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata}

### 2023-03-26 manuscript_v2/main.tex
updated discussion

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, interior hidden, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

We used data from the \emph{Survey of COVID-19 related Behaviours and
Attitudes}, a repeated cross sectional survey focused on the Canadian
province of Ontario that was commissioned by the Fields Institute for
Research in Mathematical Sciences (henceforth Fields) and the
Mathematical Modelling of COVID-19 Task Force under ethical guidance
from the University of Toronto. The survey collected socio-economic
information from participants (Table~\ref{tbl-covariates}), recorded
their location (using the nearest municipality), and asked information
on vaccination status by using the question ``Have you received the
first dose of the COVID vaccine?'', with possible answers ``yes'' and
``no''. The original dataset contained 39,029 entries (where each entry
corresponded to a unique respondent).

@@

Following an assessment of the number of entries corresponding to each
Health Region in the final dataset, only 107 observations (4.3\% of the
total) corresponded to cities located in the North West and North East
Health Regions. The low representation of these Health Regions in the
dataset is noticeable in Figure~\ref{fig-map},which shows that responses
from these areas came from a relatively low number of cities when
compared to the most populated Health Regions, such as the Toronto or
Central Regions. We omitted the North East and North East Health Regions
from further analyses due to the low number of entries. Therefore, the
total number of unique entries used for analysis was 3,551 which
included the East, Central, Toronto, and West Health Regions.

@@

The change from LHINs to Health Regions for healthcare in Ontario was
aimed at reducing healthcare
disparities\textsuperscript{\protect\hyperlink{ref-tsasis2012}{30}}. The
relatively recent nature of the change, which occurred in late 2019,
highlights the importance of studies that can determine if there are
intra-regional differences in healthcare that need to be addressed,
particularly in the context of the COVID-19 pandemic.

Our results indicate that across the most densely populated Health
Regions of Ontario, almost three quarters of the surveyed individuals
reported having received the first dose of the COVID-19 vaccine
(Table~\ref{tbl-descriptive-stats}), and that there were no significant
differences in vaccination odds among the age groups considered in the
survey. This result is consistent with overall vaccination rates
reported for Canada, which have been relatively higher when compared to
other high income
countries\textsuperscript{\protect\hyperlink{ref-dube2022}{39}}, with
vaccination uptake rates across different age groups presented in other
studies\textsuperscript{\protect\hyperlink{ref-guay2022}{19},\protect\hyperlink{ref-macdonald2021}{40}},
and with the vaccination information provided by Public Health Ontario,
which shows that for the period where the Fields survey ran (Sept 30,
2021-Jan 17, 2022) there was a minimum of 80\% of first dose vaccination
coverage among all the age groups considered in the
survey\textsuperscript{\protect\hyperlink{ref-ontario-covid}{41}}.

However, we identified intra-provincial differences in vaccination based
on socio-economic and geographical factors. First, our results show
significant differences in vaccination odds in individuals with a
household income below CAD 60,000 and in individuals belonging to
visible minority groups. Those who identified as Black, Latin American,
or belonging to a minority group not included in the survey (Southeast
Asian, Filipino, West Asian, and Minority not identified elsewhere) had
vaccination odds below 33\% when compared to individuals that identified
as White/Caucasian (Table~\ref{tbl-model}). These results are consistent
with other studies that have shown lower vaccination rates in
individuals that identify as part of a racial minority, or that have a
low household
income\textsuperscript{\protect\hyperlink{ref-guay2022}{19}--\protect\hyperlink{ref-hussain2022}{21},\protect\hyperlink{ref-carter2022}{42}}.

@@

This result is likely due to the fact that individuals that belong
racial minority groups tend to perform occupations that have been deemed
as ``essential'' in the context of the
pandemic\textsuperscript{\protect\hyperlink{ref-hawkins2020}{43},\protect\hyperlink{ref-ct2021}{44}},
which include occupations such as grocery store workers, gas station
workers, warehouse and distribution workers, and manufacturing workers,
all being occupations for which an income within the significant
brackets is to be expected. In the case of Ontario, essential workers
had priority for COVID-19
vaccination\textsuperscript{\protect\hyperlink{ref-mishra2021}{45}},
which would explain the higher odds of vaccination for these individuals
in certain income brackets, in contrast to the lower odds of vaccination
for the same type of individuals with higher household income. In other
words, it is possible that the type of occupation played an important
role in increasing the odds of vaccination in these racial minority
groups.

Additionally, significant higher vaccination odds were identified in the
West Health Region when compared to the Health Region of Toronto
(Table~\ref{tbl-model}). The West Health Region comprises the regions of
Waterloo and Niagara, the counties of Wellington, Essex and Lambton, and
the cities of Hamilton, Haldimand, Brant, and Chatham-Kent. In this
case, a possible rationale for the results is the fact that in the
survey, about 47\% of the entries for this Health Region corresponded to
White/Caucasian individuals, who reported an overall 83\% vaccination
rate (Supplementary Table A-6). However, the interaction effect of
Health Region and race was also significant in the case of individuals
identifying as South Asian or other minorities not included in the
survey Table~\ref{tbl-model}. In this case, the results of the
interaction term in the model indicate that the odds of vaccination for
those within the South Asian and Other minority groups in the West
Region decreased when compared to the other Health Regions
(Supplementary Figure A-4).

According to Ontario Health, 13.2\% of the population in the West Health
Region identifies as a visible minority, whereas 2.5\% identifies as
Indigenous\textsuperscript{\protect\hyperlink{ref-ontariohealth}{46}}.
In the case of this analysis, the estimated lower odds are likely to be
explained from a socio-economic perspective. In fact, 50\% of the
answers from this region in the survey came from the former LHINs of
Hamilton Niagara Haldimand Brant, and Erie St.~Clair, both which are
among the regions of Ontario with the highest proportion of their
population (more than 20\%) in the lowest income
quintile\textsuperscript{\protect\hyperlink{ref-buajitti2018}{47}}
(Supplementary Table A-7). Therefore, this result partly reinforces the
well-known existing association between low vaccination rates and
income, but it additionally indicates that there were intra-regional
differences in vaccination. Interestingly, a disproportionate number of
COVID-19 cases and low vaccination rate (under 50\%) have been
previously reported in the South Asian community of
Ontario\textsuperscript{\protect\hyperlink{ref-anand2022}{48}}; in this
regard, our result provides additional context by showing that within
the South Asian community, there were differences in vaccination uptake
across Ontario. Moreover, because significant lower odds of vaccination
were also identified other minority groups, this provides a rationale
for future studies that explore how vaccination uptake varies across
different minority groups within Ontario and other Canadian provinces.

There are some limitations to the present study. First, the data
collection design, which allowed respondents to withdraw from the survey
at any point, resulted in a high number of unique entries in the survey
with multiple missing answers. Because we focused on entries that had
complete observations in the covariates of interest for our analysis, it
is possible that some information was not considered by excluding
observations that had information in other variables (such as work from
home, or number of persons in the household). However, we attempted to
minimize this possibility by correcting the dataset using information
from the Census. More granular corrections, which for example could be
based on demographic information by municipality, could be used in the
future to obtain a more accurate approximation to the population totals
of the province. Moreover, our analysis did not consider the North West
and North East Health Regions, due to the low number of entries from
these areas in the survey (Figure~\ref{fig-map}). Although low
representation from these areas is based on the fact that these regions
only account for 5\% of the total population of Ontario, these regions
are the home to more than 100,000 individuals that identify as
Indigenous\textsuperscript{\protect\hyperlink{ref-ontariohealth}{46}}, a
minority group that has historically suffered from reduced access to
health care and
discrimination\textsuperscript{\protect\hyperlink{ref-mosby2021}{17}}.
Therefore, there is a need for additional studies that focus on these
low-populated Health Regions in Ontario where disparities in vaccination
might be significant and understudied.

The results in this study are based on self-reported data, where the
risk of bias exist. Despite this, because in the context of COVID-19 it
has been shown that good agreement exists between self-reported and
documented vaccination
status\textsuperscript{\protect\hyperlink{ref-stephenson2022}{49}}, the
effect of self-reported bias is likely to not be significant in this
case. Finally, it is likely that there have been differences in
vaccination across the province as more doses of the vaccine were
administered and as successive variants emerged. Because this study
focused only on vaccination status regarding the first dose of the
vaccine within a relatively short time window, it can only provide a
snapshot of the societal dynamics behind the pandemic. Nonetheless, the
results presented here can serve as a starting point to motivate future
longitudinal research that aims to quantify geographical differences
within vulnerable segments of the population, and that can be used to
inform the development of public health policies within the province of
Ontario or across other provinces that aim to minimize disparities in
health access.

@@

\leavevmode\vadjust pre{\hypertarget{ref-dube2022}{}}%
\CSLLeftMargin{39. }%
\CSLRightInline{Dubé E, Gagnon D, MacDonald N. Between persuasion and
compulsion: The case of {COVID}-19 vaccination in canada.
\emph{Vaccine}. 2022;40(29):3923-3926.
doi:\href{https://doi.org/10.1016/j.vaccine.2022.05.053}{10.1016/j.vaccine.2022.05.053}}

\leavevmode\vadjust pre{\hypertarget{ref-macdonald2021}{}}%
\CSLLeftMargin{40. }%
\CSLRightInline{MacDonald NE, Comeau J, Dubé Ève, et al. Royal society
of canada {COVID}-19 report: Enhancing {COVID}-19 vaccine acceptance in
canada. Blais JM, ed. \emph{{FACETS}}. 2021;6:1184-1246.
doi:\href{https://doi.org/10.1139/facets-2021-0037}{10.1139/facets-2021-0037}}

\leavevmode\vadjust pre{\hypertarget{ref-ontario-covid}{}}%
\CSLLeftMargin{41. }%
\CSLRightInline{{Ontario COVID-19 Data Tool}. Accessed February 27,
2023.
\url{https://www.publichealthontario.ca/en/data-and-analysis/infectious-disease/covid-19-data-surveillance/covid-19-data-tool?tab=vaccine}}

\leavevmode\vadjust pre{\hypertarget{ref-carter2022}{}}%
\CSLLeftMargin{42. }%
\CSLRightInline{Carter MA, Biro S, Maier A, Shingler C, Guan TH.
{COVID}-19 vaccine uptake in southeastern ontario, canada: Monitoring
and addressing health inequities. \emph{Journal of Public Health
Management and Practice}. 2022;28(6):615-623.
doi:\href{https://doi.org/10.1097/phh.0000000000001565}{10.1097/phh.0000000000001565}}

\leavevmode\vadjust pre{\hypertarget{ref-hawkins2020}{}}%
\CSLLeftMargin{43. }%
\CSLRightInline{Hawkins D. Differential occupational risk for {COVID}-19
and other infection exposure according to race and ethnicity.
\emph{American Journal of Industrial Medicine}. 2020;63(9):817-820.
doi:\href{https://doi.org/10.1002/ajim.23145}{10.1002/ajim.23145}}

\leavevmode\vadjust pre{\hypertarget{ref-ct2021}{}}%
\CSLLeftMargin{44. }%
\CSLRightInline{Côté D, Durant S, MacEachen E, et al. A rapid scoping
review of {COVID}-19 and vulnerable workers: Intersecting occupational
and public health issues. \emph{American Journal of Industrial
Medicine}. 2021;64(7):551-566.
doi:\href{https://doi.org/10.1002/ajim.23256}{10.1002/ajim.23256}}

\leavevmode\vadjust pre{\hypertarget{ref-mishra2021}{}}%
\CSLLeftMargin{45. }%
\CSLRightInline{Mishra S, Stall NM, Ma H, et al. \emph{A Vaccination
Strategy for Ontario {COVID}-19 Hotspots and Essential Workers}. Ontario
{COVID}-19 Science Advisory Table; 2021.
doi:\href{https://doi.org/10.47326/ocsat.2021.02.26.1.0}{10.47326/ocsat.2021.02.26.1.0}}

\leavevmode\vadjust pre{\hypertarget{ref-ontariohealth}{}}%
\CSLLeftMargin{46. }%
\CSLRightInline{\emph{{A}nnual {B}usiness {P}lan 2022/23}. Ontario
Health;
\url{https://www.ontariohealth.ca/sites/ontariohealth/files/2022-05/OHBusinessPlan22_23.pdf};
2022.}

\leavevmode\vadjust pre{\hypertarget{ref-buajitti2018}{}}%
\CSLLeftMargin{47. }%
\CSLRightInline{Buajitti E, Watson T, Kornas K, Bornbaum C, Henry D,
Rosella LC. Ontario atlas of adult mortality, 1992-2015: Trends in
{L}ocal {H}ealth {I}ntegration {N}etworks. Published online 2018.
\url{https://tspace.library.utoronto.ca/handle/1807/82836}}

\leavevmode\vadjust pre{\hypertarget{ref-anand2022}{}}%
\CSLLeftMargin{48. }%
\CSLRightInline{Anand SS, Arnold C, Bangdiwala SI, et al. Seropositivity
and risk factors for {SARS}-{CoV}-2 infection in a south asian community
in ontario: A cross-sectional analysis of a prospective cohort study.
\emph{{CMAJ} Open}. 2022;10(3):E599-E609.
doi:\href{https://doi.org/10.9778/cmajo.20220031}{10.9778/cmajo.20220031}}

\leavevmode\vadjust pre{\hypertarget{ref-stephenson2022}{}}%
\CSLLeftMargin{49. }%
\CSLRightInline{Stephenson M, Olson SM, Self WH, et al. Ascertainment of
vaccination status by self-report versus source documentation: Impact on
measuring {COVID}-19 vaccine effectiveness. \emph{Influenza and Other
Respiratory Viruses}. 2022;16(6):1101-1111.
doi:\href{https://doi.org/10.1111/irv.13023}{10.1111/irv.13023}}

>>>>

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, frame hidden, breakable, interior hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

We used data from the \emph{Survey of COVID-19 related Behaviours and
Attitudes}, a repeated cross sectional survey focused on the Canadian
province of Ontario that was commissioned by the Fields Institute for
Research in Mathematical Sciences (henceforth Fields) and the
Mathematical Modelling of COVID-19 Task Force under ethical guidance
from the University of Toronto, and which ran between September 30th,
2021 and January 17th,2022. The survey collected socio-economic
information from participants (Table~\ref{tbl-covariates}), recorded
their location (using the nearest municipality), and asked information
on vaccination status by using the question ``Have you received the
first dose of the COVID vaccine?'', with possible answers ``yes'' and
``no''. The original dataset contained 39,029 entries (where each entry
corresponded to a unique respondent).

@@

Following an assessment of the number of entries corresponding to each
Health Region in the final dataset, only 107 observations (4.3\% of the
total) corresponded to cities located in the North West and North East
Health Regions. The low representation of these Health Regions in the
dataset is noticeable in Figure~\ref{fig-map},which shows that responses
from these areas came from a relatively low number of cities when
compared to the most populated Health Regions, such as the Toronto or
Central Regions. We omitted the North East and North East Health Regions
from further analyses due to the low number of entries. Therefore, the
total number of unique entries used for analysis was 3,551 which
included the East, Central, Toronto, and West Health Regions and that
covered the period between September 30th,2021 and December 12th, 2021.

@@

There existence of healthcare disparities within Ontario is a topic of
particular interest in due to the recent change in the healthcare system
of this region, which eliminated the LHIN model and adopted larger
Health Regions system in late 2019 in an attempt to address the
disparities of the former
approach\textsuperscript{\protect\hyperlink{ref-tsasis2012}{30},\protect\hyperlink{ref-dong2022}{31}}.
In this context, analyzing COVID-19 vaccination estimates within the
province is important as they can provide an initial assessment of
variations that might need to be addressed by decision-makers.

Our results indicate that across the most densely populated Health
Regions of Ontario, almost three quarters of the surveyed individuals
reported having received the first dose of the COVID-19 vaccine
(Table~\ref{tbl-descriptive-stats}). It is worth mentioning that
province-wide vaccination rates for the period of interest are somewhat
different from those of the survey, particularly in the case of those 55
years of age and older, which in the survey had a vaccination rate of
72\%, against a rate of 88.4\% reported for the closest age bracket (50
years of age and older) reported by Public Health Ontario at the start
of the period covered by the data (between September 30th, 2021 and
December 12th,
2021)\textsuperscript{\protect\hyperlink{ref-ontario-covid}{39}}. In
this regard, differences are to be expected because the survey
represents a random sample from the population, and therefore, the
sampling process is likely to cause variations between the values from
the survey and province-wide estimates.

We believe that these differences did not have a significant impact in
our analyses, because our results indicate that there were no
significant differences in vaccination odds among the age groups
considered in the survey, in agreement with the overall vaccination
rates reported for Canada, which have been relatively higher when
compared to other high income
countries\textsuperscript{\protect\hyperlink{ref-dube2022}{40}}, and
with vaccination uptake rates across different age groups presented in
other
studies\textsuperscript{\protect\hyperlink{ref-guay2022}{19},\protect\hyperlink{ref-macdonald2021}{41}}.
Moreover, vaccination rates within each age in the dataset are in good
agreement with province-wide estimates (e.g., a rate of 95\% for those
with 61 years of age, Supplementary Table A-6). Additionally, when
overall vaccination rates for the province are disaggregated, it can be
seen that regional differences were present during the period analyzed,
which can be masked by province-wide estimates. For example, the Public
Health Unit of Lambton (a region within the West Health Region) and the
Public Health Unit of Haliburton, Kawartha, and the Pine Ridge District
(an area covered by the East Health Region) reported lower vaccination
rates (78\%) for those 50 years of age and older at the beginning of the
period of interest, whereas other regions had higher vaccination
rates\textsuperscript{\protect\hyperlink{ref-ontario-covid}{39}}. To
this day, differences in vaccination rates within the province are
present, because according to Public Health Ontario, as of March of 2023
some regions have less than 75\% vaccination
rate\textsuperscript{\protect\hyperlink{ref-ontario-covid-map}{42}}.
Overall, these reasons indicate that the estimates obtained from the
data are in good agreement with the trends from the population.

We identified significant intra-provincial differences in vaccination
based on socio-economic and geographical factors. First, our results
show differences in odds of vaccination in individuals with a household
income below CAD 60,000 and in individuals belonging to visible minority
groups. Those who identified as Arab/Middle Eastern, Black, Latin
American, or that belonged to a minority group not included in the
survey (Southeast Asian, Filipino, West Asian, and minority groups not
identified elsewhere) had vaccination odds that were less than a third
of individuals that identified as White/Caucasian
(Table~\ref{tbl-model}). These results are consistent with other studies
that have shown lower vaccination rates in individuals that identify as
part of a racial minority, or that have a low household
income\textsuperscript{\protect\hyperlink{ref-guay2022}{19}--\protect\hyperlink{ref-hussain2022}{21},\protect\hyperlink{ref-carter2022}{43}}.

@@

This result is likely due to the fact that individuals that belong
racial minority groups tend to perform occupations that have been deemed
as ``essential'' in the context of the
pandemic\textsuperscript{\protect\hyperlink{ref-hawkins2020}{44},\protect\hyperlink{ref-ct2021}{45}},
which include occupations such as grocery store workers, gas station
workers, warehouse and distribution workers, and manufacturing workers,
all being occupations for which an income within the significant
brackets is to be expected. In the case of Ontario, essential workers
had priority for COVID-19
vaccination\textsuperscript{\protect\hyperlink{ref-mishra2021}{46}},
which would explain the higher odds of vaccination for these individuals
in certain income brackets, in contrast to the lower odds of vaccination
for the same type of individuals with higher household income. In other
words, it is possible that the type of occupation played an important
role in increasing the odds of vaccination in these racial minority
groups.

Additionally, significant higher vaccination odds were identified in the
West Health Region when compared to the Health Region of Toronto
(Table~\ref{tbl-model}). The West Health Region comprises the regions of
Waterloo and Niagara, the counties of Wellington, Essex and Lambton, and
the cities of Hamilton, Haldimand, Brant, and Chatham-Kent. In this
case, a possible rationale for the results is the fact that in the
survey, about 47\% of the entries for this Health Region corresponded to
White/Caucasian individuals, who reported an overall 83\% vaccination
rate (Supplementary Table A-7). However, the interaction effect of
Health Region and race was also significant in the case of individuals
identifying as South Asian or other minorities not included in the
survey Table~\ref{tbl-model}. In this case, the results of the
interaction term in the model indicate that the odds of vaccination for
those within the South Asian and Other minority groups in the West
Region decreased when compared to the other Health Regions
(Supplementary Figure A-4).

According to Ontario Health, 13.2\% of the population in the West Health
Region identifies as a visible minority, whereas 2.5\% identifies as
Indigenous\textsuperscript{\protect\hyperlink{ref-ontariohealth}{47}}.
In the case of this analysis, the estimated lower odds are likely to be
explained from a socio-economic perspective. In fact, 50\% of the
answers from this region in the survey came from the former LHINs of
Hamilton Niagara Haldimand Brant, and Erie St.~Clair, both which are
among the regions of Ontario with the highest proportion of their
population (more than 20\%) in the lowest income
quintile\textsuperscript{\protect\hyperlink{ref-buajitti2018}{48}}
(Supplementary Table A-8). Therefore, this result partly reinforces the
well-known existing association between low vaccination rates and
income, but it additionally indicates that there were intra-regional
differences in vaccination. Interestingly, a disproportionate number of
COVID-19 cases and low vaccination rate (under 50\%) have been
previously reported in the South Asian community of
Ontario\textsuperscript{\protect\hyperlink{ref-anand2022}{49}}; in this
regard, our result provides additional context by showing that within
the South Asian community, there were differences in vaccination uptake
across Ontario. Moreover, because significant lower odds of vaccination
were also identified other minority groups, this provides a rationale
for future studies that explore how vaccination uptake varies across
different minority groups within Ontario and other Canadian provinces.

There are some limitations to the present study. First, the data
collection design, which allowed respondents to withdraw from the survey
at any point, resulted in a high number of unique entries in the survey
with multiple missing answers. Because we focused on entries that had
complete observations in the covariates of interest for our analysis, it
is possible that some information was not considered by excluding
observations that had information in other variables (such as work from
home, or number of persons in the household). However, we attempted to
minimize this possibility by correcting the dataset using information
from the Census. More granular corrections, which for example could be
based on demographic information by municipality, could be used in the
future to obtain a more accurate approximation to the population totals
of the province. Moreover, our analysis did not consider the North West
and North East Health Regions, due to the low number of entries from
these areas in the survey (Figure~\ref{fig-map}). Although low
representation from these areas is based on the fact that these regions
only account for 5\% of the total population of Ontario, these regions
are the home to more than 100,000 individuals that identify as
Indigenous\textsuperscript{\protect\hyperlink{ref-ontariohealth}{47}}, a
minority group that has historically suffered from reduced access to
health care and
discrimination\textsuperscript{\protect\hyperlink{ref-mosby2021}{17}}.
Therefore, there is a need for additional studies that focus on these
low-populated Health Regions in Ontario where disparities in vaccination
might be significant and understudied.

The results in this study are based on self-reported data, where there
is a risk that biased values are reported. Despite this, because in the
context of COVID-19 it has been shown that good agreement exists between
self-reported and documented vaccination
status\textsuperscript{\protect\hyperlink{ref-stephenson2022}{50}}, and
therefore, the effect of self-reported bias is likely to not be
significant in our analyses. Finally, it is likely that there have been
differences in vaccination across the province as more doses of the
vaccine were administered and as successive variants emerged. Because
this study focused only on vaccination status regarding the first dose
of the vaccine within a relatively short time window, it can only
provide a snapshot of the societal dynamics behind the pandemic.
Nonetheless, the results presented here can serve as a starting point to
motivate the collection of robust longitudinal data that can be used to
quantify geographical and temporal differences within vulnerable
segments of the population, and that can be used to inform the
development of adequate public health policies within the province of
Ontario or across other provinces that aim to minimize disparities in
health access.

@@

\leavevmode\vadjust pre{\hypertarget{ref-ontario-covid}{}}%
\CSLLeftMargin{39. }%
\CSLRightInline{{Ontario COVID-19 Data Tool}. Accessed February 27,
2023.
\url{https://www.publichealthontario.ca/en/data-and-analysis/infectious-disease/covid-19-data-surveillance/covid-19-data-tool?tab=vaccine}}

\leavevmode\vadjust pre{\hypertarget{ref-dube2022}{}}%
\CSLLeftMargin{40. }%
\CSLRightInline{Dubé E, Gagnon D, MacDonald N. Between persuasion and
compulsion: The case of {COVID}-19 vaccination in canada.
\emph{Vaccine}. 2022;40(29):3923-3926.
doi:\href{https://doi.org/10.1016/j.vaccine.2022.05.053}{10.1016/j.vaccine.2022.05.053}}

\leavevmode\vadjust pre{\hypertarget{ref-macdonald2021}{}}%
\CSLLeftMargin{41. }%
\CSLRightInline{MacDonald NE, Comeau J, Dubé Ève, et al. Royal society
of canada {COVID}-19 report: Enhancing {COVID}-19 vaccine acceptance in
canada. Blais JM, ed. \emph{{FACETS}}. 2021;6:1184-1246.
doi:\href{https://doi.org/10.1139/facets-2021-0037}{10.1139/facets-2021-0037}}

\leavevmode\vadjust pre{\hypertarget{ref-ontario-covid-map}{}}%
\CSLLeftMargin{42. }%
\CSLRightInline{{Ontario COVID-19 Data Tool}. Accessed March 24, 2023.
\url{https://www.publichealthontario.ca/en/data-and-analysis/infectious-disease/covid-19-data-surveillance/covid-19-data-tool?tab=maps}}

\leavevmode\vadjust pre{\hypertarget{ref-carter2022}{}}%
\CSLLeftMargin{43. }%
\CSLRightInline{Carter MA, Biro S, Maier A, Shingler C, Guan TH.
{COVID}-19 vaccine uptake in southeastern ontario, canada: Monitoring
and addressing health inequities. \emph{Journal of Public Health
Management and Practice}. 2022;28(6):615-623.
doi:\href{https://doi.org/10.1097/phh.0000000000001565}{10.1097/phh.0000000000001565}}

\leavevmode\vadjust pre{\hypertarget{ref-hawkins2020}{}}%
\CSLLeftMargin{44. }%
\CSLRightInline{Hawkins D. Differential occupational risk for {COVID}-19
and other infection exposure according to race and ethnicity.
\emph{American Journal of Industrial Medicine}. 2020;63(9):817-820.
doi:\href{https://doi.org/10.1002/ajim.23145}{10.1002/ajim.23145}}

\leavevmode\vadjust pre{\hypertarget{ref-ct2021}{}}%
\CSLLeftMargin{45. }%
\CSLRightInline{Côté D, Durant S, MacEachen E, et al. A rapid scoping
review of {COVID}-19 and vulnerable workers: Intersecting occupational
and public health issues. \emph{American Journal of Industrial
Medicine}. 2021;64(7):551-566.
doi:\href{https://doi.org/10.1002/ajim.23256}{10.1002/ajim.23256}}

\leavevmode\vadjust pre{\hypertarget{ref-mishra2021}{}}%
\CSLLeftMargin{46. }%
\CSLRightInline{Mishra S, Stall NM, Ma H, et al. \emph{A Vaccination
Strategy for Ontario {COVID}-19 Hotspots and Essential Workers}. Ontario
{COVID}-19 Science Advisory Table; 2021.
doi:\href{https://doi.org/10.47326/ocsat.2021.02.26.1.0}{10.47326/ocsat.2021.02.26.1.0}}

\leavevmode\vadjust pre{\hypertarget{ref-ontariohealth}{}}%
\CSLLeftMargin{47. }%
\CSLRightInline{\emph{{A}nnual {B}usiness {P}lan 2022/23}. Ontario
Health;
\url{https://www.ontariohealth.ca/sites/ontariohealth/files/2022-05/OHBusinessPlan22_23.pdf};
2022.}

\leavevmode\vadjust pre{\hypertarget{ref-buajitti2018}{}}%
\CSLLeftMargin{48. }%
\CSLRightInline{Buajitti E, Watson T, Kornas K, Bornbaum C, Henry D,
Rosella LC. Ontario atlas of adult mortality, 1992-2015: Trends in
{L}ocal {H}ealth {I}ntegration {N}etworks. Published online 2018.
\url{https://tspace.library.utoronto.ca/handle/1807/82836}}

\leavevmode\vadjust pre{\hypertarget{ref-anand2022}{}}%
\CSLLeftMargin{49. }%
\CSLRightInline{Anand SS, Arnold C, Bangdiwala SI, et al. Seropositivity
and risk factors for {SARS}-{CoV}-2 infection in a south asian community
in ontario: A cross-sectional analysis of a prospective cohort study.
\emph{{CMAJ} Open}. 2022;10(3):E599-E609.
doi:\href{https://doi.org/10.9778/cmajo.20220031}{10.9778/cmajo.20220031}}

\leavevmode\vadjust pre{\hypertarget{ref-stephenson2022}{}}%
\CSLLeftMargin{50. }%
\CSLRightInline{Stephenson M, Olson SM, Self WH, et al. Ascertainment of
vaccination status by self-report versus source documentation: Impact on
measuring {COVID}-19 vaccine effectiveness. \emph{Influenza and Other
Respiratory Viruses}. 2022;16(6):1101-1111.
doi:\href{https://doi.org/10.1111/irv.13023}{10.1111/irv.13023}}
